### 2016-06-25 writing/ppabstract/PP2016Abstract_Tannock.tex
PP presentation

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{question}[theorem]{Question}
\newtheorem{example}[theorem]{Example}

@@

When we consider avoidance of a pattern, \(p\), inside a permutation class we gain
additional restrictions on the occurrences of \(p\).
We will restrict the set of permutations that form the basis
for our permutation class to a single classical pattern, \(\pi\), which we shall
refer to as the \emph{dominating pattern}. In particular, we consider the case
where \(p\) is mesh pattern of length \(2\) and \(\pi\) is either of the classical
permutation patterns \(231\) or \(321\).

By use of previous results of Claesson, Tenner and Ulfarsson\cite{ABH}
we can begin to reduce the number of potential coincidences by only looking for
coincidences between patterns that are not coincident outwith the setting of
having a dominating pattern. This gives us an initial upper bound of \(220\)
coincidence classes in each of the four cases we consider.

@@

We then go on to consider Wilf-equivalences between non-classical permutation
classes where we avoid the classical permutation pattern \(\perm{2,3,1}\) and
a mesh pattern of length \(2\). I order to establish these Wilf-equivalences
we use the results of the prior section as well as some observations about
symmetries in order to reduce the initial upper bound on Wilf-equivalence classes.
Using the bijection between avoiders of the vincular pattern
\textpattern{}{2,3,1}{1/0,1/1,1/2,1/3} and set partitions presented by
Claesson\cite{A}, and structural decomposition of avoiders to obtain generating
functions we fully classify the Wilf-equivalences. This results in \(13\)
non-trivial (\ie{} not containing only a single coincidence class) Wilf-equivalence
classes. When using generating function methods we also provide enumeration of
the non-classical permutation class.

\begin{example}
  The following patterns are experimentally Wilf-equivalent up to length 10 in
\(\av{\perm{2,3,1}}\)
\begin{equation*}
    m_1 = \pattern{}{1,2}{1/0,1/1,1/2,2/0,2/1} \text{ and }
    m_2 = \pattern{}{2,1}{0/1,1/0,1/1,1/2,2/1}
\end{equation*}
Considering structural decomposition of an avoider of \(m_1\) in \(\av{2,3,1}\)
around the leftmost point, we find that the set of avoiders has form
\begin{equation*}
    \mathcal{M}_1 = \varepsilon \sqcup
    \decompleft{0/1,1/0}{\mathcal{M}_1}{}{}{\mathcal{M}^\prime_1}
\end{equation*}
Where \(\mathcal{M}^\prime_1\) is a permutation avoiding \(\perm{2,3,1}, m_1\)
and \(\textpattern{}{1}{0/0,0/1,1/0}\), these permutations have form
\(\mathcal{M}^\prime_1\)
\begin{equation*}
    \mathcal{M}^\prime_1 = \varepsilon \sqcup
    \decompleft{0/1,1/0}{\scriptstyle \mathcal{M}_1\setminus\varepsilon}{}{}{\mathcal{M}^\prime_1}
\end{equation*}
The avoiders of \(m_2\) in \(\av{2,3,1}\) can be split in a similar manner
around the leftmost point. This gives us that both of these sets have generating
function \(M(x)\) satisfying
\begin{align}
    M(x) &= 1 + xM(x)M^\prime(x) \label{eqn:Pgen}\\
    M^\prime(x) &= 1 + x(M(x)-1)M^\prime(x)\label{eqn:PprimeGen}
 \end{align}

@@

% \talkJointWork{Christian Bean and Henning Ulfarsson}

>>>>

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{question}[theorem]{Question}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

@@

When we consider avoidance of a pattern, \(p\), inside a permutation class we gain
additional restrictions on the occurrences of \(p\).
We will restrict the set of permutations that form the basis
for our permutation class to a single classical pattern, \(\pi\), which we shall
refer to as the \emph{dominating pattern}. In particular, we consider the case
where \(p\) a is mesh pattern of length \(2\) and \(\pi\) is either of the classical
permutation patterns \(231\) or \(321\).

By use of previous results of Claesson, Tenner and Ulfarsson~\cite{ABH}
we can begin to reduce the number of potential coincidences by only looking for
coincidences between patterns that are not coincident before considering the
setting of having a dominating pattern. This gives us an initial upper bound of
\(220\) coincidence classes in each of the four cases we consider, in Table~\ref{tab:domclasses}.

@@

We then go on to consider Wilf-equivalences between non-classical permutation
classes where we avoid the permutation pattern \(\perm{2,3,1}\) and
a mesh pattern of length \(2\). In order to establish these Wilf-equivalences
we use the results of the prior section as well as some observations about
symmetries in order to reduce the initial upper bound on Wilf-equivalence classes.
Using the bijection between avoiders of the vincular pattern
\textpattern{}{2,3,1}{1/0,1/1,1/2,1/3} and set partitions presented by
Claesson~\cite{A}, and structural decomposition of avoiders to obtain generating
functions we fully classify the Wilf-equivalences. This results in \(13\)
non-trivial (\ie{} not containing only a single coincidence class) Wilf-equivalence
classes. When using generating function methods we also provide enumeration of
the non-classical permutation classes.

\begin{example}
  The following patterns are experimentally Wilf-equivalent up to length 10 in
\(\av{\perm{2,3,1}}\)
\begin{equation*}
    m_1 = \pattern{}{1,2}{1/0,1/1,1/2,2/0,2/1} \text{ and }
    m_2 = \pattern{}{2,1}{0/1,1/0,1/1,1/2,2/1}
\end{equation*}
    Considering structural decomposition of an avoider of \(m_1\) in \(\av{\perm{2,3,1}}\)
around the leftmost point, we find that the set of avoiders has form
\begin{equation*}
    \mathcal{M}_1 = \varepsilon \sqcup
    \decompleft{0/1,1/0}{\mathcal{M}_1}{}{}{\mathcal{M}^\prime_1}
\end{equation*}
Where \(\mathcal{M}^\prime_1\) is a permutation avoiding \(\perm{2,3,1}, m_1\)
and \(\textpattern{}{1}{0/0,0/1,1/0}\), these permutations have form
\(\mathcal{M}^\prime_1\)
\begin{equation*}
    \mathcal{M}^\prime_1 = \varepsilon \sqcup
    \decompleft{0/1,1/0}{\scriptstyle \mathcal{M}_1\setminus\varepsilon}{}{}{\mathcal{M}^\prime_1}
\end{equation*}
    The avoiders of \(m_2\) in \(\av{\perm{2,3,1}}\) can be split in a similar manner
around the leftmost point. This gives us that both of these sets have generating
function \(M(x)\) satisfying
\begin{align}
    M(x) &= 1 + xM(x)M^\prime(x) \label{eqn:Pgen}\\
    M^\prime(x) &= 1 + x(M(x)-1)M^\prime(x)\label{eqn:PprimeGen}
 \end{align}

@@

\talkJointWork{Henning Ulfarsson}

### 2016-06-25 writing/pppresentation/coincidences.tex
PP presentation

\section{Coincidence Classes}
\label{sec:Coincidence Classes}
\subsection{Coincidence}
\label{sub:Coincidence}
\begin{frame}{Coincidence}
  \begin{definition}
    Two mesh patterns are said to be \emph{coincident} if they are avoided by the
    same set of permutations at every length.
  \end{definition}
  \begin{block}{}
    Distinct classical patterns can never be coincident.

    Coincidences of mesh patterns of length \(2\) are classified.

@@

\subsection{Summary of Experimental Results}
\label{sub:Summary of Experimental Results}
\begin{frame}{Experimental Results}
  \begin{block}{}
  \begin{table}[htb]
\begin{center}
\begin{tabularx}{\textwidth}{c|Y|Y|Y|Y|}
\cline{2-5}
& \multicolumn{4}{|c|}{Dominating Pattern}\\
\cline{2-5}
& \multicolumn{2}{|c|}{\(\perm{2,3,1}\)}&\multicolumn{2}{|c|}{\(\perm{3,2,1}\)}\\
\cline{2-5}
& \(\perm{1,2}\)&\(\perm{2,1}\)&\(\perm{1,2}\)&\(\perm{2,1}\)\\
\hline
\multicolumn{1}{|r|}{No Dominating rule}&\(220\)&\(220\)&\(220\)&\(220\)\\
\hline
\multicolumn{1}{|r|}{\hspace{0pt}\invisible<2->{First Dominating rule}}&\hspace{0pt}\invisible<2->{\(85\)}&\hspace{0pt}\invisible<2->{\(43\)}&\hspace{0pt}\invisible<2->{\(220\)}&\hspace{0pt}\invisible<2->{\(29\)}\\
\hline
\multicolumn{1}{|r|}{\hspace{0pt}\invisible<2->{Second Dominating rule}}&\hspace{0pt}\invisible<2->{\(59\)}&\hspace{0pt}\invisible<2->{\(39\)}&\hspace{0pt}\invisible<2->{\(220\)}&\hspace{0pt}\invisible<2->{\(29\)}\\
\hline
\multicolumn{1}{|r|}{\hspace{0pt}\invisible<2->{Third Dominating rule}}&\hspace{0pt}\invisible<2->{\(56\)}&\hspace{0pt}\hspace{0pt}\invisible<2->{\(39\)}&\hspace{0pt}\invisible<2->{\(220\)}&\hspace{0pt}\hspace{0pt}\invisible<2->{\(29\)}\\
\hline
\multicolumn{1}{|r|}{Experimental class size}&\(56\)&\(39\)&\(213\)&\(29\)\\
\hline
\end{tabularx}
\end{center}
    \caption{Coincidence class number reduction by application of Dominating rules}
    \label{tab:domclasses}
\end{table}
\end{block}
\end{frame}

@@

\begin{frame}{Experimental Results}
  \begin{block}{}
  \begin{table}[htb]
\begin{center}
\begin{tabularx}{\textwidth}{c|Y|Y|Y|Y|}
\cline{2-5}
& \multicolumn{4}{|c|}{Dominating Pattern}\\
\cline{2-5}
& \multicolumn{2}{|c|}{\(\perm{2,3,1}\)}&\multicolumn{2}{|c|}{\(\perm{3,2,1}\)}\\
\cline{2-5}
& \(\perm{1,2}\)&\(\perm{2,1}\)&\(\perm{1,2}\)&\(\perm{2,1}\)\\
\hline
\multicolumn{1}{|r|}{No Dominating rule}&\(220\)&\(220\)&\(220\)&\(220\)\\
\hline
\multicolumn{1}{|r|}{First Dominating rule}&\(85\)&\(43\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{\hspace{0pt}\invisible{Second Dominating rule}}&\hspace{0pt}\invisible{\(59\)}&\hspace{0pt}\invisible{\(39\)}&\hspace{0pt}\invisible{\(220\)}&\hspace{0pt}\invisible{\(29\)}\\
\hline
\multicolumn{1}{|r|}{\hspace{0pt}\invisible{Third Dominating rule}}&\hspace{0pt}\invisible{\(56\)}&\hspace{0pt}\hspace{0pt}\invisible{\(39\)}&\hspace{0pt}\invisible{\(220\)}&\hspace{0pt}\hspace{0pt}\invisible{\(29\)}\\
\hline
\multicolumn{1}{|r|}{Experimental class size}&\(56\)&\(39\)&\(213\)&\(29\)\\
\hline
\end{tabularx}
\end{center}
    \caption{Coincidence class number reduction by application of Dominating rules}
\end{table}
\end{block}
\end{frame}

@@

\begin{frame}
  \begin{lemma}
    Given a mesh pattern \(m =(\sigma, R)\), where the box \((a,b)\) is not
in \(R\), and a dominating classical pattern \(\pi = (\pi,\emptyset)\) if
\(\pi \preceq \adda{\sigma}{(a,b)}\)\\
,then in any occurrence of \(m\) in a permutation \(\varrho\), the region
corresponding to the box \((a,b)\) can only contain an decreasing
subsequence of \(\varrho\).
  \end{lemma}
\end{frame}

@@

\begin{frame}{Experimental Results}
  \begin{block}{}
  \begin{table}[htb]
\begin{center}
\begin{tabularx}{\textwidth}{c|Y|Y|Y|Y|}
\cline{2-5}
& \multicolumn{4}{|c|}{Dominating Pattern}\\
\cline{2-5}
& \multicolumn{2}{|c|}{\(\perm{2,3,1}\)}&\multicolumn{2}{|c|}{\(\perm{3,2,1}\)}\\
\cline{2-5}
& \(\perm{1,2}\)&\(\perm{2,1}\)&\(\perm{1,2}\)&\(\perm{2,1}\)\\
\hline
\multicolumn{1}{|r|}{No Dominating rule}&\(220\)&\(220\)&\(220\)&\(220\)\\
\hline
\multicolumn{1}{|r|}{First Dominating rule}&\(85\)&\(43\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{Second Dominating rule}&\(59\)&\(39\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{\hspace{0pt}\invisible{Third Dominating rule}}&\hspace{0pt}\invisible{\(56\)}&\hspace{0pt}\invisible{\(39\)}&\hspace{0pt}\invisible{\(220\)}&\hspace{0pt}\invisible{\(29\)}\\
\hline
\multicolumn{1}{|r|}{Experimental class size}&\(56\)&\(39\)&\(213\)&\(29\)\\
\hline
\end{tabularx}
\end{center}
    \caption{Coincidence class number reduction by application of Dominating rules}
\end{table}
\end{block}
\end{frame}

@@

\begin{frame}{Experimental Results}
  \begin{block}{}
  \begin{table}[htb]
\begin{center}
\begin{tabularx}{\textwidth}{c|Y|Y|Y|Y|}
\cline{2-5}
& \multicolumn{4}{|c|}{Dominating Pattern}\\
\cline{2-5}
& \multicolumn{2}{|c|}{\(\perm{2,3,1}\)}&\multicolumn{2}{|c|}{\(\perm{3,2,1}\)}\\
\cline{2-5}
& \(\perm{1,2}\)&\(\perm{2,1}\)&\(\perm{1,2}\)&\(\perm{2,1}\)\\
\hline
\multicolumn{1}{|r|}{No Dominating rule}&\(220\)&\(220\)&\(220\)&\(220\)\\
\hline
\multicolumn{1}{|r|}{First Dominating rule}&\(85\)&\(43\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{Second Dominating rule}&\(59\)&\(39\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{Third Dominating rule}&\(56\)&\(39\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{Experimental class size}&\(56\)&\(39\)&\(213\)&\(29\)\\
\hline
\end{tabularx}
\end{center}
    \caption{Coincidence class number reduction by application of Dominating rules}
\end{table}
\end{block}
\end{frame}

\subsection{Special Cases}
\label{sub:Special Cases}
\begin{frame}{Special Cases}
  There are \(7\) coincidences of the form \(\av{\perm{3,2,1},m}\) that are not
  explained by the rules.
  \begin{example}
    \begin{equation*}
      m_1 = \pattern{}{1,2}{0/1,0/2,2/0,2/1} \text{ and } m_2 = \pattern{}{1,2}{0/1,0/2,1/1,2/0,2/1}
    \end{equation*}
    This coincidence is explained by mathematical induction on the number of
    points in the region corresponding to the middle box.
  We call this number \(n\).
  \end{example}
\end{frame}
\begin{frame}
  \begin{example}
    \begin{description}
    \only<1-2>{\item [Base Case \((n=0)\):] The base case holds since we can freely shade the
        box if it contains no points.}
    \only<2>{\item [Inductive Hypothesis \((n=k)\):] Suppose that we can find an occurrence
        of the second pattern if we have an occurrence of the first with \(k\) points
        in the middle box.}
    \only<3>{\item [Inductive Step \((n=k+1)\)] Suppose that we have \((k+1)\) points in
        the middle box. Choose the bottom most point in the middle box, this gives the
        mesh pattern
     \begin{equation*}
        \begin{tikzpicture}[scale=0.5]
            \modpattern[5]{}{1,2,3}{0/1,0/2,0/3,1/1,2/1,3/0,3/1,3/2}
            \draw (2.5,0.5) node {\(X\)};
        \end{tikzpicture}
    \end{equation*}
        Now we need to consider the box labelled \(X\). If this box is empty then
        we have an occurrence of \(m_2\) and are done.}
        \only<4>{\item [Inductive Step \((n=k+1)\) (cont.)] If this box contains
        any points then we gain some extra shading on the mesh pattern
        due to the dominating pattern
     \begin{equation*}
        \begin{tikzpicture}[scale=0.5]
            \modpattern[5]{2,3}{1,2,3}{0/1,0/2,0/3,1/1,1/2,1/3,2/1,3/0,3/1,3/2}
            \filldraw (2.5,0.5) circle (4 pt);
        \end{tikzpicture}
    \end{equation*}
        The two highlighted points form an occurrence of \(m_1\) with \(k\)
        points in the middle box, and thus by the Inductive Hypothesis we
        are done.}
\end{description}
  \end{example}
\end{frame}

>>>>

\section{Coincidence Classes}
\label{sec:Coincidence Classes}
\subsection{Coincidence}
\label{sub:Coincidence}
\begin{frame}{Coincidence}
  % \begin{definition}
  %   Two mesh patterns are said to be \emph{coincident} if they are avoided by the
  %   same set of permutations at every length.
  % \end{definition}
  \begin{block}{}
    % Distinct classical patterns can never be coincident.
    %
    Coincidences of mesh patterns of length \(2\) are classified.

@@

\subsection{Summary of Experimental Results}
\label{sub:Summary of Experimental Results}
\begin{frame}{Experimental Results}
  \begin{block}{}
  \begin{table}[htb]
\begin{center}
\begin{tabularx}{\textwidth}{c|Y|Y|Y|Y|}
\cline{2-5}
& \multicolumn{4}{|c|}{Dominating Pattern}\\
\cline{2-5}
    & \multicolumn{2}{|c|}{\(\av{\perm{2,3,1}}\)}&\multicolumn{2}{|c|}{\(\av{\perm{3,2,1}}\)}\\
\cline{2-5}
& \(\perm{1,2}\)&\(\perm{2,1}\)&\(\perm{1,2}\)&\(\perm{2,1}\)\\
\hline
\multicolumn{1}{|r|}{No Dominating rule}&\(220\)&\(220\)&\(220\)&\(220\)\\
\hline
\multicolumn{1}{|r|}{\hspace{0pt}\invisible<2->{First Dominating rule}}&\hspace{0pt}\invisible<2->{\(85\)}&\hspace{0pt}\invisible<2->{\(43\)}&\hspace{0pt}\invisible<2->{\(220\)}&\hspace{0pt}\invisible<2->{\(29\)}\\
\hline
\multicolumn{1}{|r|}{\hspace{0pt}\invisible<2->{Second Dominating rule}}&\hspace{0pt}\invisible<2->{\(59\)}&\hspace{0pt}\invisible<2->{\(39\)}&\hspace{0pt}\invisible<2->{\(220\)}&\hspace{0pt}\invisible<2->{\(29\)}\\
\hline
\multicolumn{1}{|r|}{\hspace{0pt}\invisible<2->{Third Dominating rule}}&\hspace{0pt}\invisible<2->{\(56\)}&\hspace{0pt}\hspace{0pt}\invisible<2->{\(39\)}&\hspace{0pt}\invisible<2->{\(220\)}&\hspace{0pt}\hspace{0pt}\invisible<2->{\(29\)}\\
\hline
\multicolumn{1}{|r|}{Experimental class size}&\(56\)&\(39\)&\(213\)&\(29\)\\
\hline
\end{tabularx}
\end{center}
    \caption{Coincidence class number reduction by application of Dominating rules}
    \label{tab:domclasses}
\end{table}
\end{block}
\end{frame}

@@

\begin{frame}{Experimental Results}
  \begin{block}{}
  \begin{table}[htb]
\begin{center}
\begin{tabularx}{\textwidth}{c|Y|Y|Y|Y|}
\cline{2-5}
& \multicolumn{4}{|c|}{Dominating Pattern}\\
\cline{2-5}
    & \multicolumn{2}{|c|}{\(\av{\perm{2,3,1}}\)}&\multicolumn{2}{|c|}{\(\av{\perm{3,2,1}}\)}\\
\cline{2-5}
& \(\perm{1,2}\)&\(\perm{2,1}\)&\(\perm{1,2}\)&\(\perm{2,1}\)\\
\hline
\multicolumn{1}{|r|}{No Dominating rule}&\(220\)&\(220\)&\(220\)&\(220\)\\
\hline
\multicolumn{1}{|r|}{First Dominating rule}&\(85\)&\(43\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{\hspace{0pt}\invisible{Second Dominating rule}}&\hspace{0pt}\invisible{\(59\)}&\hspace{0pt}\invisible{\(39\)}&\hspace{0pt}\invisible{\(220\)}&\hspace{0pt}\invisible{\(29\)}\\
\hline
\multicolumn{1}{|r|}{\hspace{0pt}\invisible{Third Dominating rule}}&\hspace{0pt}\invisible{\(56\)}&\hspace{0pt}\hspace{0pt}\invisible{\(39\)}&\hspace{0pt}\invisible{\(220\)}&\hspace{0pt}\hspace{0pt}\invisible{\(29\)}\\
\hline
\multicolumn{1}{|r|}{Experimental class size}&\(56\)&\(39\)&\(213\)&\(29\)\\
\hline
\end{tabularx}
\end{center}
    \caption{Coincidence class number reduction by application of Dominating rules}
\end{table}
\end{block}
\end{frame}

@@

\begin{frame}
  \begin{lemma}
    Given a mesh pattern \(m =(\sigma, R)\), where the box \((a,b)\) is not
in \(R\), and a dominating classical pattern \(\pi = (\pi,\emptyset)\) if
\(\pi \preceq \adda{\sigma}{(a,b)}\),
then in any occurrence of \(m\) in a permutation \(\varrho\), the region
corresponding to the box \((a,b)\) can only contain an decreasing
subsequence of \(\varrho\).
  \end{lemma}
\end{frame}

@@

\begin{frame}{Experimental Results}
  \begin{block}{}
  \begin{table}[htb]
\begin{center}
\begin{tabularx}{\textwidth}{c|Y|Y|Y|Y|}
\cline{2-5}
& \multicolumn{4}{|c|}{Dominating Pattern}\\
\cline{2-5}
    & \multicolumn{2}{|c|}{\(\av{\perm{2,3,1}}\)}&\multicolumn{2}{|c|}{\(\av{\perm{3,2,1}}\)}\\
\cline{2-5}
& \(\perm{1,2}\)&\(\perm{2,1}\)&\(\perm{1,2}\)&\(\perm{2,1}\)\\
\hline
\multicolumn{1}{|r|}{No Dominating rule}&\(220\)&\(220\)&\(220\)&\(220\)\\
\hline
\multicolumn{1}{|r|}{First Dominating rule}&\(85\)&\(43\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{Second Dominating rule}&\(59\)&\(39\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{\hspace{0pt}\invisible{Third Dominating rule}}&\hspace{0pt}\invisible{\(56\)}&\hspace{0pt}\invisible{\(39\)}&\hspace{0pt}\invisible{\(220\)}&\hspace{0pt}\invisible{\(29\)}\\
\hline
\multicolumn{1}{|r|}{Experimental class size}&\(56\)&\(39\)&\(213\)&\(29\)\\
\hline
\end{tabularx}
\end{center}
    \caption{Coincidence class number reduction by application of Dominating rules}
\end{table}
\end{block}
\end{frame}

@@

\begin{frame}{Experimental Results}
  \begin{block}{}
  \begin{table}[htb]
\begin{center}
\begin{tabularx}{\textwidth}{c|Y|Y|Y|Y|}
\cline{2-5}
& \multicolumn{4}{|c|}{Dominating Pattern}\\
\cline{2-5}
    & \multicolumn{2}{|c|}{\(\av{\perm{2,3,1}}\)}&\multicolumn{2}{|c|}{\(\av{\perm{3,2,1}}\)}\\
\cline{2-5}
& \(\perm{1,2}\)&\(\perm{2,1}\)&\(\perm{1,2}\)&\(\perm{2,1}\)\\
\hline
\multicolumn{1}{|r|}{No Dominating rule}&\(220\)&\(220\)&\(220\)&\(220\)\\
\hline
\multicolumn{1}{|r|}{First Dominating rule}&\(85\)&\(43\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{Second Dominating rule}&\(59\)&\(39\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{Third Dominating rule}&\(56\)&\(39\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{Experimental class size}&\(56\)&\(39\)&\(213\)&\(29\)\\
\hline
\end{tabularx}
\end{center}
    \caption{Coincidence class number reduction by application of Dominating rules}
\end{table}
\end{block}
\end{frame}

\subsection{Special Cases}
\label{sub:Special Cases}
\begin{frame}{Special Cases}
  There are \(7\) coincidences of the form \(\av{\perm{3,2,1},m}\) that are not
  explained by the rules.
  \begin{example}
    \begin{equation*}
      m_1 = \pattern{}{1,2}{0/1,0/2,2/0,2/1} \text{ and } m_2 = \pattern{}{1,2}{0/1,0/2,1/1,2/0,2/1}
    \end{equation*}
    This coincidence is explained by mathematical induction on the number of
    points in the region corresponding to the middle box.
  We call this number \(n\).
  \end{example}
\end{frame}
\begin{frame}
  \begin{example}
    \begin{equation*}
      m_1 = \pattern{}{1,2}{0/1,0/2,2/0,2/1}
    \end{equation*}
    \begin{description}
    \only<1-2>{\item [Base Case \((n=0)\):] The base case holds since we can freely shade the
        box if it contains no points.}
    \only<2>{\item [Inductive Hypothesis \((n=k)\):] Suppose that we can find an occurrence
        of the second pattern if we have an occurrence of the first with \(k\) points
        in the middle box.}
    \only<3>{\item [Inductive Step \((n=k+1)\)] Suppose that we have \((k+1)\) points in
        the middle box. Choose the bottom most point in the middle box, this gives the
        mesh pattern
     \begin{equation*}
        \begin{tikzpicture}[scale=0.5]
            \modpattern[5]{}{1,2,3}{0/1,0/2,0/3,1/1,2/1,3/0,3/1,3/2}
            \draw (2.5,0.5) node {\(X\)};
        \end{tikzpicture}
    \end{equation*}
        Now we need to consider the box labelled \(X\). If this box is empty then
        we have an occurrence of \(m_2\) and are done.}
        \only<4>{\item [Inductive Step \((n=k+1)\) (cont.)] If this box contains
        any points then we gain some extra shading on the mesh pattern
        due to the dominating pattern
     \begin{equation*}
        \begin{tikzpicture}[scale=0.5]
            \modpattern[5]{2,3}{1,2,3}{0/1,0/2,0/3,1/1,1/2,1/3,2/1,3/0,3/1,3/2}
            \filldraw (2.5,0.5) circle (4 pt);
        \end{tikzpicture}
    \end{equation*}
        The two highlighted points form an occurrence of \(m_1\) with \(k\)
        points in the middle box, and thus by the Inductive Hypothesis we
        are done.}
\end{description}
  \end{example}
\end{frame}
